---
title: "Olympic Games"
format:
  dashboard:
    scrolling: false
    orientation: columns
    nav-buttons: [github]
    github: https://github.com/JohnGavin/mine-cetinkaya-rundel-olympicdash
logo: images/olympics-logo.svg
logo-alt: Olympics logo - 5 rings
callout-appearance: default # default minimal simple
callout-icon: true
---

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(gt)
```
# test pg

## Row {.tabset}

### note

::: {#nte-example .callout-note}
#| title: callout-note
Note that there are five types of callouts, including:
`note`, `warning`, `important`, `tip`, and `caution`.
:::

::: {#nte-example2 .callout-note icon=false}
#| title: callout-note2

### Pay Attention

Using callouts is an effective way to highlight content that your reader give special consideration or attention.

:::


### tip

::: {#tip-example .callout-tip}
#| title: callout-tip
### Cross-Referencing a Tip

Add an ID starting with `#tip-` to reference a tip.
:::

See @tip-example...

::: {.callout-tip  collapse="true"}
#| title: callout-tip
## Tip with Title

This is an example of a callout with a title.
:::


### caution

::: {#cau-example .callout-caution collapse="true"}
#| title: callout-caution

## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::

### important

::: {#imp-example .callout-important collapse="true"}
#| title: callout-important

## Expand To Learn About important

This is an example of a 'folded' important callout that can be expanded by the user.
:::

### warning

::: {#wrn-example .callout-warning collapse="true"}
#| title: callout-warning

## Expand To Learn About warning

This is an example of a 'folded' important callout that can be expanded by the user.
:::




# Olympic Games

```{r}
#| label: load-data
#| message: false
olympics_full <- read_csv("data/olympics.csv")
```

```{r}
#| label: prep-data
olympics <-
  olympics_full |>
  filter(
    season == "Summer",
    !is.na(medal)
  ) |>
  separate_wider_delim(
    cols = team,
    names = c("team", "suffix"),
    delim = "-",
    too_many = "merge",
    too_few = "align_start"
  ) |>
  select(-suffix) |>
  mutate(medal = fct_relevel(medal, "Bronze", "Silver", "Gold"))
```


## Columns
### Row - Medals by sport {height="80%"}

```{r}
#| title: Medals by sport
olympics |>
  mutate(
    sport = fct_lump_n(sport, n = 15),
    sport = fct_infreq(sport),
    sport = fct_rev(sport),
    sport = fct_relevel(sport, "Other", after = 0)
  ) |>
  ggplot(aes(y = sport, fill = medal)) +
  geom_bar() +
  guides(fill = guide_legend(reverse = TRUE)) +
  labs(
    x = NULL,
    y = NULL,
    fill = "Medal"
  ) +
  theme_minimal() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.9, 0.2),
    legend.direction = "horizontal",
    legend.background = element_rect(fill = "white", color = "gray")
  )
```

### Row - Medals by year {height="20%"}

```{r}
#| title: Medals by year
olympics |>
  count(year, medal) |>
  ggplot(aes(x = year, y = n, color = medal)) +
  geom_point(size = 0.5) +
  geom_line() +
  guides(color = guide_legend(reverse = TRUE)) +
  scale_x_continuous(breaks = seq(1896, 2020, 8)) +
  labs(
    x = "Year",
    y = NULL,
    color = "Medal"
  ) +
  theme_minimal() +
  theme(
    legend.position = "inside",
    legend.position.inside = c(0.9, 0.2),
    legend.direction = "horizontal",
    legend.background = element_rect(fill = "white", color = "gray")
  )
```

## Medals by country

```{r}
#| title: Medals by country
olympics |>
  count(team, medal) |>
  pivot_wider(names_from = medal, values_from = n, values_fill = 0) |>
  mutate(Total = Bronze + Gold + Silver) |>
  relocate(Team = team, Gold, Silver, Bronze, Total) |>
  arrange(desc(Total), Team) |>
  gt()
```


## Row asdf

See @nte-example...\
See @tip-example...\
See @nte-example2 ...\
See @cau-example ...\
See @imp-example ...\
See @wrn-example ...\
